%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass{resume_long} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\usepackage[pdftex]{hyperref}
\hypersetup{
    pdftitle = {CV Gurkirt Singh},
    pdfauthor = {Gurkirt Singh}
}
\name{Gurkirt Singh} % Your name
% \address{Vison and Media Lab, Simon Fraser University, Burnaby, Canada} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\jobaddress{Xovis AG – Bern, Switzerland}

\address{guru094@gmail.com \\ http://gurkirt.github.io/ \\ +41 - 779 774 271 \\ B-Permit (open)}

\begin{document}


%----------------------------------------------------------------------------------------
%	Experience SECTION
%----------------------------------------------------------------------------------------
 
\begin{rSection}{Experience}{\quad Academia: 4+ years, Industry 4+ years}

  \begin{rSubsections}{Xovis AG}{Bern, CH,}{Senior ML \& CV Engineer}{Since Oct 23, 2 years}{
    Distillation: Led the design and development of model distillation pipeline. \\
    -- Distilled Transformer models (ViT) to embedded deployment firendly models. \\
    Object Detection: Spearheaded the design and development of multi-task object detection and tracking models. \\
    -- Achieved three times reduction in false postive rate. \\
    Quantization: Engineered QAT for WinogradConvs to enable deployment on 250K+ embedded devices with FPGA. \\
    Auto-labeling: Led efforts to optimize and semi-automate the labeling pipeline. \\
    Multi-modal foundation models: Implemented SSL techniques to train multi-modal foundation models using large quantity unlabeled videos.
    }\end{rSubsections}
  \begin{rSubsections}{ETH}{Zurich, CH,}{Postdoctoral Fellow}{Feb 20, 3.5 years }{
    Responsible for research support for startups with problems such as monocular depth estimation,\\ 3D reconstruction, 3D human pose estimation, and MRI classification.}\end{rSubsections}
  \begin{rSubsections}{BorealisAI}{Vancouver, CA,}{Research Intern}{Feb 19, 4 months}{
    Developed human-object relation detection algorithm for videos.}\end{rSubsections}
  \begin{rSubsections}{Disney Research}{Pittsburgh, US,}{Research Intern}{Feb 17, 6 months}{
    Developed action-detection method for meta-data generation of ABC's tv-episodes.}\end{rSubsections}
  \begin{rSubsections}{Siemens Research}{Banglore, IN,}{Research Engineer}{Oct 13, 2 years}{
    Support research team with implementation of algorithms such as optical-flow and object-tracking.}\end{rSubsections}
  \begin{rSubsections}{INRIA}{Grenoble, FR,}{Research Intern}{Feb 13, 8 months}{Researched on gesture recognition method for RGB-D cameras.}\end{rSubsections}
  % \begin{rSubsections}{IIT}{Delhi, IN,}{Research Assistant}{May 11, 1 year}\end{rSubsections}
  % \begin{rSubsections}{IIT}{Kanpur, IN,}{Research Assistant}{Jul 10, 8 months}\end{rSubsections}
  \begin{rSubsections}{University of Edinburgh}{UK,}{Research Intern}{Jan 10, 4 months}{Worked on anomalous trajectory detection with GMMs.}\end{rSubsections}
    % \vspace{-0.08in}
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}{}

    % {\bf \footnotesize{Oxford Brookes University}} \hfill {\em \footnotesize{Sept. 2015 - Nov 2019}} 
    % \\ \footnotesize{Ph.D. Student}; \footnotesize{Supervised by Prof. Fabio Cuzzolin}
    % {\bf Institut Polytechnique de Grenoble, France} \hfill {\em Sep. 2012 - Jun. 2013} 
    % \\ \footnotesize{MSc in Informatics at ENSIMAG}; \footnotesize{Advised by Prof. Radu Horaud \& Dr. Georgios Evangelidis}
    % % \vspace{-0.08in}
    % {\bf VIT University, Vellore, India} \hfill {\em Aug. 2006 - May 2010} 
    % \\ \footnotesize{B.Tech}; \footnotesize{Advised by Prf. Bob Fisher \& Prof. Arulmozhivarman Pachiyappan}

\begin{eSubsection}{Oxford Brookes University}{UK}{PhD Computer Vision}{Sep 15, 4 years}\end{eSubsection}
\begin{eSubsection}{ENSIMAG, INP}{Grenoble, FR}{MSc Informatics}{Sep 12 - 1.2 years}\end{eSubsection}
\begin{eSubsection}{VIT University}{Vellore, IN}{B.Tech Electronics}{Aug 06 - 4 years}\end{eSubsection} 

\end{rSection}
% \vspace{0.1in}
% \begin{rSection}{Research Interests/Expertise}{}

% \begin{tabular}{@{\hspace{6ex}}l  @{\hspace{6ex}}l} %% @{} >{\bfseries}l @{\hspace{6ex}} l }
% %Machine Learning &  Graph Co Model, Unsupervised Learning, \\&specializing in Latent Variable Models \& Variational Inference \\
% Large scale detection, segmentation and tracking & Spatiotemporal action detection \\ 
% Monocular depth estimation and 3D reconstruction & 3D human pose-estimation \\
% \end{tabular}

% \end{rSection}


%----------------------------------------------------------------------------------------
%	Publication and research projects SECTION
%----------------------------------------------------------------------------------------
\vspace{0.1in}
\begin{rSection}{Selected Publications}{18+\footnotesize{ in TPAMI, ICCV, CVPRW, ECCVW, WACV, ACCV, BMVC, ICPR}}
%------------------------------------------------

\small{\textbf{Gurkirt Singh}, Vasileios Choutas, Suman Saha, Fisher Yu, Luc Van Gool},
\textbf{Spatio-Temporal Action Detection Under Large Motion},
\textit{\small{IEEE/CVF Winter Conference on Applications of computer Vision (WACV), 2023}}

%-----------------------------------------------
% \vspace{-0.03in}
\small{\textbf{Gurkirt Singh}, Stephen Akrigg, Manuele Di Maio, .... others \&,
% , Valentina Fontana, Reza Javanmard Alitappeh, Salman Khan, Suman Saha, Kossar Jeddisaravi, Farzad Yousefi, Jacob Culley, Tom Nicholson, Jordan Omokeowa, Salman Khan, Stanislao Grazioso, Andrew Bradley, Giuseppe Di Gironimo, 
Fabio Cuzzolin},
\textbf{ROAD: The ROad Event Awareness Dataset for Autonomous Driving},
\textit{\small{IEEE Transactions on Pattern Analysis and Machine Intelligence (TPAMI), 2022}}


% \vspace{-0.03in}
% \small{Vivek Singh Bawa, \textbf{Gurkirt Singh}, Francis KapingA, .... others \&, 
% %  Inna Skarga-Bandurova, Alice Leporini, Carmela Landolfo, Armando Stabile, Francesco Setti, Riccardo Muradore, Elettra Oleari, 
% Fabio Cuzzolin},
% \textbf{ESAD: Endoscopic Surgeon Action Detection Dataset},
% \textit{\small{Preprint arXiv: 2006.07164, 2021}}

\vspace{-0.03in}
\small{Suman Saha, \textbf{Gurkirt Singh}, Michael Sapienza, Philip HS Torr, Fabio Cuzzolin}
\textbf{Spatio-Temporal Action Instance Segmentation and Localisation}
\textit{\small{Book Chapter: Modelling Human Motion, 2020}}

\vspace{-0.03in}
\small{\textbf{Gurkirt Singh} and Fabio Cuzzolin},
\textbf{Recurrent Convolutions for Causal 3D CNNs},
\textit{\small{Workshop on Large Scale Holistic Video Understanding, ICCV, 2019}}

\vspace{-0.03in}
\small{Silvio Olivastri, \textbf{Gurkirt Singh} and Fabio Cuzzolin},
\textbf{An End-to-End Baseline for Video Captioning},
\textit{\small{Workshop on Large Scale Holistic Video Understanding, ICCV, 2019}}

% %-----------------------------------------------
% \vspace{-0.03in}
% \textbf{Action Detection from a Robot-Car Perspective}
% \vspace{-0.08in}
% \small{\textbf{Gurkirt Singh}${}^*$, Stephen Akrigg${}^*$, Valentina Fontana${}^*$, 
% Manuele Di Maio, Suman Saha, Fabio Cuzzolin}
% \vspace{-0.08in}
% \textit{\small{Preprint arXiv: 1807.11332, 2018}}

% %------------------------------------------------
\vspace{-0.03in}
\small{\textbf{Gurkirt Singh}, Suman Saha and Fabio Cuzzolin},
\textbf{TraMNet - Transition Matrix Network for Efficient Action Tube Proposals},
\textit{\small{Asian Conference on Computer Vision (ACCV), 2018}}


% %------------------------------------------------
% \vspace{0.03in}
% \small{Harkirat Behl, Michael Sapienza \textbf{Gurkirt Singh}, Suman Saha, Fabio Cuzzolin and Philip Torr},
% \textbf{Incremental Tube Construction for Human Action Detection},
% \textit{\small{British Machine Vision Conference (BMVC), 2018}}


% %------------------------------------------------
% \vspace{-0.03in}
% \small{\textbf{Gurkirt Singh}, Suman Saha and Fabio Cuzzolin},
% \textbf{Predicting Action Tubes},
% \textit{\small{Workshop on Anticipating Human Behavior, ECCV 2018}}


% %------------------------------------------------
\vspace{-0.03in}
\small{\textbf{Gurkirt Singh}, Suman Saha, Michael Sapienza, Philip Torr and Fabio Cuzzolin},
\textbf{Online Real-time Multiple Spatiotemporal Action Localisation and Prediction},
\textit{\small{International Conference on Computer Vision (ICCV), 2017}}


% %------------------------------------------------
\vspace{-0.03in}
\textbf{AMTnet: Action-Micro-Tube Regression by end-to-end Trainable Deep Architecture},
\small{Suman Saha, \textbf{Gurkirt Singh} and Fabio Cuzzolin},
\textit{\small{International Conference on Computer Vision (ICCV), 2017}}


% %-----------------------------------------------
\vspace{-0.03in}
\small{Suman Saha, \textbf{Gurkirt Singh}, Michael Sapienza, Philip Torr and Fabio Cuzzolin},
\textbf{Deep Learning for Detecting Multiple Space-Time Action Tubes in Videos},
\textit{\small{British Machine Vision Conference (BMVC), 2016}}

%------------------------------------------------
% \vspace{-0.03in}
% \small{\textbf{Gurkirt Singh} and Fabio Cuzzolin},
% \textbf{Untrimmed Video Classification for Activity Detection: Submission to ActivityNet Challenge},
% \textit{\small{ActivityNet Challenge Workshop, CVPR 2016}}


%------------------------------------------------
\vspace{-0.03in}
\small{Georgios Evangelidis, \textbf{Gurkirt Singh}, Radu Horaud},
\textbf{Skeletal Quads: Human action recognition using joint quadruples},
\textit{\small{International Conference on Pattern Recognition Vision (ICPR), 2014}}


% \vspace{-0.03in}
% \small{Georgios Evangelidis, \textbf{Gurkirt Singh}, Radu Horaud},
% \textbf{Continuous Gesture Recognition from Articulated Poses},
% \textit{\small{Workshop on Looking at People (Chalearn), ECCV 2014}}


% %------------------------------------------------
% \textbf{Frame-wise Representations of Depth Videos for Action Recognition}
% \vspace{-0.08in}
% \small{\textbf{Gurkirt Singh}}
% \vspace{-0.08in}
% \textit{\small{Master's thesis, Grenoble INP, 2013}}
% %------------------------------------------------
% \textbf{Categorising the Abnormal Behaviour from an Indoor Overhead Camera}
% \vspace{-0.08in}
% \small{\textbf{Gurkirt Singh}}
% \vspace{-0.08in}
% \textit{\small{Bachelor's thesis, VIT University, 2010}}

\end{rSection}

% \vspace{0.1in}
% ---------------
\begin{rSection}{Awards \& Challenges}{} \itemsep -2pt
  % \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
\item \textbf{Multisports-Challenge, DeeperAction ECCV'22}: Winner of Action Detection Track \hfill 2022
\item \textbf{Doctoral Consortium}: Selected for Doctoral Consortium Award ICCV-2019 \hfill 2019
\item \textbf{Best Reviewer}: Selected as the best reviewer for ICCV-2019 \hfill 2019
\item \textbf{PhD Scholarship}: 150th Anniversary PhD Scholarship, Oxford Brookes University \hfill 2015
\item \textbf{Charades-Challenge 2017}: Acton Recognition and Segmentation tasks (Rank: 2/10 and 3/6) \hfill 2017
\item \textbf{ActivityNet-Challenge 2017}: Classification tasks (Rank 3/29)  \hfill 2017
\item \textbf{ActivityNet-Challenge 2016}: Classification and Detection tasks (Rank 10/24 and 2/6) \hfill 2016
\item \textbf{Chalearn-Challenge 2014}: Looking at People Challenge (Gesture Detection Task Rank 7/17) \hfill 2014
%Chalearn Multi-Modal Gesture Recognition Challenge (Rank 17/54) \hfill 2013
% \end{tabular}
\end{rSection}


% \vspace{0.1in}
\begin{rSection}{Skills}{} \itemsep -2pt
\item  \textbf{Programming}: Python, Matlab, C/C++, Lua
\item  \textbf{Deep Learning Platforms}: PyTorch, JAX, Torch, Caffe, TensorFlow, Keras
\item  \textbf{Libraries}: Numpy, Scipy, Scikit-Learn, OpenCV, Eigen, Kinect SDK, Wandb
\item  \textbf{Operating Systems}: Linux, macOS, Windows
% \item  \textbf{Development Environments:} VS code, Eclipse, Spyder, Pycharm.
\end{rSection}

\vspace{0.1in}
\begin{rSection}{Teaching Experience}{} \itemsep -2pt
  \item  \textbf{Machine Learning}: Teaching Assistant (Postgraduate) \hfill 2018
  \item  \textbf{Computer Vision and Machine Learning}: Guest lecturer (Postgraduate) \hfill 2016, 2017, 2018
  \item  \textbf{Understanding Programming}: Lab Assistant (Undergraduate)  \hfill 2015, 2016, 2017
\end{rSection}

\clearpage

\vspace{0.1in}
\begin{rSection}{Community Contributions}{} \itemsep -2pt
    \item Co-cognised workshop on The ROAD Challenge ICCV 2023.
    \item Co-cognised workshop on The ROAD Challenge ICCV 2021.
    \item Co-cognised workshop on ESAD challenge for surgeon action detection, MIDL 2020.
    \item Best reviewer award ICCV 2019
    \item Reviewer: TPAMI 2017, 2018, ICCV 2019, 2021, ECCV 2020, 2022 CVPR 2018,2019,2020,2021,2022 BMVC 2018,2019 and IJCIA 2017, 2018, 2019
\end{rSection}


\vspace{0.1in}
\begin{rSection}{Languages}{}  \itemsep -2pt
  English (C1), German (A2) Punjabi (Maternal), Hindi (Maternal)
\end{rSection}

\vspace{0.1in}
\begin{rSection}{References}{}  \itemsep -2pt
\item \href{https://ee.ethz.ch/the-department/faculty/professors/person-detail.OTAyMzM=.TGlzdC80MTEsMTA1ODA0MjU5.html}{Professor Luc Van Gool}, ETH Zurich, Switzerland.
\item \href{http://cms.brookes.ac.uk/staff/FabioCuzzolin/}{Professor Fabio Cuzzolin}, Oxford Brookes University, UK.
\item \href{https://www.cs.ubc.ca/~lsigal/}{Professor Leonid Sigal}, University of British Columbia, Canada.
\item \href{http://www.robots.ox.ac.uk/~phst/}{Professor Philip Torr}, University of Oxford, UK.
\item \href{https://team.inria.fr/perception/team-members/evangelidis/}{Dr. Georgios Evangelidis}; Snap, Vienna, Austria.
\item \href{https://ps.is.tuebingen.mpg.de/person/alehrmann}{Dr. Andreas Lehrmann}, BorealisAI, Vancouver, Canada.
\item \href{http://homepages.inf.ed.ac.uk/rbf/}{Professor Bob Fisher}, University of Edinburgh, UK.
% \item \href{https://team.inria.fr/perception/team-members/radu-patrice-horaud/}{Professor Radu Patrice HORAUD}, INRIA, Grenoble, France.
\item \href{http://www.cfar.umd.edu/~kale/}{Dr. Amit Kale}, Bosch Research, India.
\end{rSection}

\vspace{0.1in}
\begin{rSection}{More Information}{}  \itemsep -2pt
  \item \textbf{Google Scholar}: \url{https://scholar.google.com/citations?user=w8XHUMIAAAAJ&hl=en}
  \item \textbf{Homepage}: \url{http://gurkirt.github.io/}
  \item \textbf{Github}: \url{https://github.com/gurkirt}
  \item \textbf{LinkdIn}: \url{https://www.linkedin.com/in/gurkirt/}
\end{rSection}


\end{document}